---
title: "Assignment 1 - Data Acquisition and Management, Fall 2020"
author: "Arushi Arora"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library (readr)

urlfile="https://raw.githubusercontent.com/fivethirtyeight/covid-19-polls/9e9f5bbb6dd62a5d35e886488c5771bfe9c80821/covid_approval_polls.csv"

rawdata<-read_csv(url(urlfile))

polls_data <- rawdata[,c("start_date","end_date","pollster","sponsor","sample_size","population","text","approve","disapprove") ]



```

## How Americans View The Coronavirus Crisis And Trump's Response
Link: https://projects.fivethirtyeight.com/coronavirus-polls/

## Overview


The article reports on data collected from polls on whether Americans approve 
          or disapprove of Trumps response to the pandemic. The approval rates to his 
          response were stratified by party affliation.
          The article has also reported numbers on the level of concern in Americans 
          regarding COVID-19 and its impact on the economy.


## Findings
Based on an average of different polls, it is clear that
about two-thirds disapprove of Trumps response to the pandemic while thirty-eight percent approved of his response. On a party basis, most approvals came from Republicans (79.3%) while only 8.5% of Democrats approved of his response.


## Dataset
covid_approval_polls.csv

```{r Polls_data}
polls_data
```

## Recommendations
We can also look at whether the differences between approval and disapproval
by party are significant or not (not reported in the article). It will give a sense of whether the differences are by chance or if its just noise. It would be interesting to note which income groups support/approve Trumps response versus those that dont and whether the level of concerns about the infection are lower in the same income group that report low concerns?